### 2015-02-07 Article/Article.tex
06_02_2015

\subsection*{Case 4: several plant species and several resources}

In this section, we present the general case of the model, where herbivores compete for multiple resources embedded into multiple plants. Assuming that nutrient quotas differ among plant species, the consumption of a given plant is not equivalent to consumption of another plant. As in case 2, herbivores may control their diet by allocating more time/energy to feed on specific plants rather than others. Therefore, each herbivore may find a specific pathway to collect resources \citep{Simpson1995, Raubenheimer1999}. The foraging strategy of a given herbivore is graphically represented by the consumption vector, which is the combination of the consumption vectors for all the plant species consumed. As a consequence, the slope of the consumption vector depends on the foraging strategy of the herbivore, which can adjust the slope by consuming more efficiently a given species versus the others. Thus, niche segregation among herbivore species is a combination of segregation in space (as in case 2) and segregation on the requirements (as in case 3). As we shall see, this niche segregation allows for coexistence of multiple herbivores on multiple resources. \par
To simplify, we consider here the case of two herbivores competing for two plants embedding two resources (see appendix 4 for details). The resource supply is represented in the phase plan by the supply point S, which is the total amount of resources at equilibrium in plants 1 and 2, in absence of consumption:
\begin{equation}
S_{R1}=Q_{v1R1}(S_{v1}-a\barre{V}_1)+Q_{v2R1}(S_{v2}-a\barre{V}_2)
\end{equation}
\begin{equation}
S_{R2}=Q_{v1R2}(S_{v1}-a\barre{V}_1)+Q_{v2R2}(S_{v2}-a\barre{V}_2)
\end{equation}
For a given herbivore $i$, the ZNGI slope ($\alpha|_{Ru}$) for each resource ($R_u$) is:
\begin{equation}\label{alpha}
\alpha|_{Ru}=\frac{\barre{V}_1|_{Ru}Q_{v1R2}+\barre{V}_2|_{Ru}Q_{v2R2}}{\barre{V}_1|_{Ru}Q_{v1R1}+\barre{V}_2|_{Ru}Q_{v2R1}}
\end{equation}
Note that the slope depends on $\{ \barre{V}_1,\barre{V}_2\}$, which themselves depend both on the herbivore and the plant parameters (including the supply parameters). Hence, the ZNGI slope is not parallel to the axis. \par

>>>>

\subsection*{Competition for several plant species and several resources}

In this section, we present the general case of the model, where herbivores compete for multiple resources embedded into multiple plants. Assuming that nutrient quotas differ among plant species, the consumption of a given plant is not equivalent to consumption of another plant. Due to spatial segregation among resources, herbivores may control their diet by allocating more time/energy to feed on specific plants rather than others. Therefore, each herbivore may find a specific pathway to collect resources \citep{Simpson1995, Raubenheimer1999}. The foraging strategy of a given herbivore is graphically represented by the consumption vector, which is the combination of the consumption vectors for all the plant species consumed. As a consequence, the slope of the consumption vector depends on the foraging strategy of the herbivore, which can adjust the slope by consuming more efficiently a given species versus the others. Thus, niche segregation among herbivore species is a combination of spatial segregation and segregation on the requirements. As we shall see, this niche segregation allows for coexistence of multiple herbivores on multiple resources. \par
To simplify, we consider here the case of two herbivores competing for two plants embedding two resources (see appendix 4 for details). The resource supply is represented in the phase plan by the supply point S, which is the total amount of resources at equilibrium in plants 1 and 2, in absence of consumption:
\begin{equation}
S_{R1}=Q_{v1R1}(S_{v1}-a\barre{V}_1)+Q_{v2R1}(S_{v2}-a\barre{V}_2)
\end{equation}
\begin{equation}
S_{R2}=Q_{v1R2}(S_{v1}-a\barre{V}_1)+Q_{v2R2}(S_{v2}-a\barre{V}_2)
\end{equation}
For a given herbivore $i$, the ZNGI slope ($\alpha|_{Ru}$) for each resource ($R_u$) is:
\begin{equation}\label{alpha}
\alpha|_{Ru}=\frac{\barre{V}_1|_{Ru}Q_{v1R2}+\barre{V}_2|_{Ru}Q_{v2R2}}{\barre{V}_1|_{Ru}Q_{v1R1}+\barre{V}_2|_{Ru}Q_{v2R1}}
\end{equation}
Note that the slope depends on $\{ \barre{V}_1,\barre{V}_2\}$, which themselves depend both on the herbivore and the plant parameters (including the supply parameters). Hence, the ZNGI slope is not parallel to the axis. \par
